Measuring the dust opacity of the debris disk around HD 107146 with transit photometry

### 2023-09-29 src/tex/ms.tex
[showyourwork] overleaf sync

% \begin{figure*}[ht]
%     \centering
%     \includegraphics[width=17cm]{figures/GS03.jpg}
%     \caption{Left: Epoch 0+1 AQ image of the HD 107146 debris ring fully sampled with the Vermin galaxy well separated beyond the periphery of the disk. Linear display range $\pm 0.05$ counts per second per pixel to show the structure of remaining PSF-subtraction residuals without saturating at the radius of highest surface brightness while also revealing the low level of “pixel to pixel” noise in the sky background at the field boundaries.  Middle: Model disk image at same display stretch derived from all eight epochs with galaxy masked. Right: Representative surface brightness radial profile/cross-section (arbitrarily along disk major axis) comparison of AQ image (solid line) vs. model comparison (dot-dashed line) showing excellent agreement at $r > 65$ pixels ($3.3”$) in region of interest of galaxy reflex motion at epochs 0 – 7 inclusive.}
%     \label{fig:GS03}
% \end{figure*}

>>>>

\begin{figure*}[ht]
    \centering
    \includegraphics[width=17cm]{figures/GS03.jpg}
    \caption{Left: Epoch 0+1 AQ image of the HD 107146 debris ring fully sampled with the Vermin galaxy well separated beyond the periphery of the disk. Linear display range $\pm 0.05$ counts per second per pixel to show the structure of remaining PSF-subtraction residuals without saturating at the radius of highest surface brightness while also revealing the low level of ``pixel to pixel'' noise in the sky background at the field boundaries.  Middle: Model disk image at same display stretch derived from all eight epochs with galaxy masked. Right: Representative surface brightness radial profile/cross-section (arbitrarily along disk major axis) comparison of AQ image (solid line) vs. model comparison (dot-dashed line) showing excellent agreement at $r > 65$ pixels ($3.3''$) in region of interest of galaxy reflex motion at epochs 0 – 7 inclusive.}
    \label{fig:GS03}
\end{figure*}
